\subsection{Objectives}

The objectives behind making a prototype for the Internship Management System, were clearly laid out before any form of implementation was started.


The main objective of the prototype was to provide a demonstration of the proposed design of the System to the clients. The prototype was used by the team to display proposed used cases for the system in a simple manner.
The team would use the prototype to give the clients of the system a walk through of the proposed design.


A second objective of the prototype was to support the gathering of requirements of the system. When giving the clients of the system a walk through it was hoped that the prototype would provide very helpful in resolving any ambiguities or inconsistencies in the requirements that the team had gathered.


The third goal of the prototype was to investigate the feasibility of the system which had been designed. The prototype was hoped to be able to be developed quickly, and would be able to show that the main requirements of the Internship Management System were achievable. The team hoped that the prototype would provide a solid proof of concept for the design that they had developed.


The final objective of the prototype was to hopefully provide a strong foundation for the main development of the project. The team hoped that if the client responded positively to the proposed design, the prototype Internship Management System could be used as a central focus for the software development system of the larger system.
