The School of Computing Science are looking for a unified system for 
collecting, reviewing, and publishing internship advertisements. There are 
some main features which the system must possess: 

Submission of internship advertisements;

Review, comment, and publication of the internship advertisements;

Viewing of internship advertisements;

Notification of successful internship applications.

The system does not have to support the actual application process, students
are to use the companies own channels for this.

Companies wishing to submit advertisements to the system are required to first
contact the course coordinator for access to the system. This ensures no fake
or spam advertisements can be submitted.

Only textual data can be submitted as part of an advertisement. There are no
strict guidelines for advertisement content so as a result, no automatic checks
on the content can be done by the system, only manually by the course
coordinator. The only possible check may be to ensure no duplicate entries
to the system, this is because companies with multiple vacancies for the same
job are only allowed a single advertisement which states the number of
available positions.

Each advertisement has to be reviewed and accepted by the course coordinator
prior to submission for students to view. As part of the review process, the
course coordinator can comment on the advertisement, either for another member
of staff to look at prior to submission or as part of feedback to be sent back
to the company. In the event of an application being rejected, the system is
not required to submit feedback to the company, this is to be done separately
by the course coordinator.

When an internship advertisement has been reviewed and published, students 
are to be notified somehow. This can be done either by mass email or via a 
notification presented to the user on login to the system.

The system is available for all Computing Science students to access and 
they are all free to apply for any internship available however SE/ESE students
are required to apply for SE/ESE suitable internships. The course coordinator is
responsible for adding this statement to the advertisement prior to publication.
The login process will be linked with existing student accounts and thus be
handled separately to the system.

Students will have a status to allow the course coordinator to track progress
through the system. A student can either be accepted into an internship, pending
approval/response to an internship application, or yet to apply/no current 
application in progress.
