\begin{UseCaseTemplate}
\UseCaseLabel{Student Logs into system}
\UseCaseDescription{A student from the University of Glasgow
  interested in applying for a summer placement/internship gains
  access to the system by logging in.}
\UseCaseRationale{A student should be able to log into the
  system. This gives the system added protection and privacy to those
  who should not have access to the system.}
\UseCasePriority{High}
\UseCaseStatus{}
\UseCaseActors{Student}
\UseCaseExtensions{}
\UseCaseIncludes{}
\UseCaseConditions{}
\UseCaseNonFunctionalRequirements{}
\UseCaseScenarios{Successful log in, Unsuccessful log in.}
\UseCaseRisks{Unable to link with GUID log in which may mean students
  have to enrol for service. }
\UseCaseUserInterface{Log in screen.}
\end{UseCaseTemplate}

\begin{UseCaseTemplate}
\UseCaseLabel{Notification of new placement}
\UseCaseDescription{When a new placement is accepted by the course
  coordinator, all student in Level 3 CS should be notified of it by 
  email.}
\UseCaseRationale{A useful feature to aid CS students in their search
  for a placement}
\UseCasePriority{Medium}
\UseCaseStatus{Uncomplete}
\UseCaseActors{Student, Course Coordinator}
\UseCaseExtensions{}
\UseCaseIncludes{}
\UseCaseConditions{}
\UseCaseNonFunctionalRequirements{}
\UseCaseScenarios{Notification Sent}
\UseCaseRisks{Handeling the response from an email being sent to a 
  non-existent email address or to an email address that causes a 
  bounceback/send fail message. A student neglecting to view emails
  sent by the service due to mass emails sent when many advertisements
  go live on one day.}
\UseCaseUserInterface{Course Coordinator Advert View Screen.}
\end{UseCaseTemplate}

\begin{UseCaseTemplate}
\UseCaseLabel{Student Views Application}
\UseCaseDescription{A student of the School of Computing Science can
  view a list of placements/internships and also see more details of a
  specific placement/internship}
\UseCaseRationale{A student will need to view all of the
  advertisements for this application to have merit, and finding out
  more information about these advertisements is also helpful.}
\UseCasePriority{High}
\UseCaseStatus{}
\UseCaseActors{Student}
\UseCaseExtensions{}
\UseCaseIncludes{Student Logs into System. Company Posts Application. }
\UseCaseConditions{}
\UseCaseNonFunctionalRequirements{}
\UseCaseScenarios{Student views all advertisements, Student views
  specific advertisement.}
\UseCaseRisks{Advertisement may not be deleted immediately after a
  successful applicant has been found so a student may apply for an
  advertisement that is no longer available.}
\UseCaseUserInterface{Application View Screen.}
\end{UseCaseTemplate}

\begin{UseCaseTemplate}
\UseCaseLabel{Company Submits Application}
\UseCaseDescription{A potential employer will submit an advertisement
  for review by the Course Coordinator.}
\UseCaseRationale{The submission must be available for any placements
  to make their way onto the system after review by the Course Coordinator}
\UseCasePriority{High}
\UseCaseStatus{Incomplete Information}
\UseCaseActors{Company}
\UseCaseExtensions{}
\UseCaseIncludes{}
\UseCaseConditions{}
\UseCaseNonFunctionalRequirements{}
\UseCaseScenarios{Application is submitted for review.}
\UseCaseRisks{A submission may be in an incorrect format that will not
  be accepted by the Course Coordinator and may cause the company time
  by having to redesign the advertisement - this may put some companys
  off posting an advertisement.}
\UseCaseUserInterface{Application Submission Screen.}
\end{UseCaseTemplate}

\begin{UseCaseTemplate}
\UseCaseLabel{Company Edits Application}
\UseCaseDescription{A potential employer can edit an advertisement.}
\UseCaseRationale{The terms or specific details of an advertisement may
  change during the time the advert is active so the company must be
  able to edit this information.}
\UseCasePriority{Medium}
\UseCaseStatus{Incomplete Information}
\UseCaseActors{Company, Course Coordinator.}
\UseCaseExtensions{Company Submits Application. Course Coordinator
  Reviews Advertisement.}
\UseCaseIncludes{}
\UseCaseConditions{Cannot edit an application that is not yet active.}
\UseCaseNonFunctionalRequirements{}
\UseCaseScenarios{Company Edits Application.}
\UseCaseRisks{We do not know if the application has to be reviewed after
  the edit has been made - this does make sense as if the edit was not
  reviewed then the company could change the edit to something that is
  no longer suitable. We do not know if there is a limit to the number
  of edits the company can make before another advertisement has to be
  submitted.}
\UseCaseUserInterface{Course Coordinator Advertisement View Screen, 
  Application Submission Screen.}
\end{UseCaseTemplate}

\begin{UseCaseTemplate}
\UseCaseLabel{Course Coordinator Reviews Advertisement}
\UseCaseDescription{As the original specification, the Course
  Coordinator must review each individual advertisement before
  publishing for viewing by students.}
\UseCaseRationale{Specified inside the original specification.}
\UseCasePriority{High}
\UseCaseStatus{Incomplete Information}
\UseCaseActors{Course Coordinator}
\UseCaseExtensions{}
\UseCaseIncludes{Company Submits Application}
\UseCaseConditions{}
\UseCaseNonFunctionalRequirements{}
\UseCaseScenarios{Application passes review. Application fails review.}
\UseCaseRisks{We currently do not know what the criteria for
  applications are (except from there are no images). We do not know
  what, if any, feedback is given to the applicants if they pass/fail
  the review process.}
\UseCaseUserInterface{Course Coordinator Advertisement View Screen.}
\end{UseCaseTemplate}

\begin{UseCaseTemplate}
\UseCaseLabel{Student Notifies Course Coordinator of Successful 
  Application}
\UseCaseDescription{As the original specification, a successful student
  must notify the course coordinator of their success and this must be
  added to the database.}
\UseCaseRationale{Specified inside the original specification.}
\UseCasePriority{High}
\UseCaseStatus{Incomplete Information}
\UseCaseActors{Course Coordinator. Student}
\UseCaseExtensions{Student Logs into System.}
\UseCaseIncludes{Company Submits Application}
\UseCaseConditions{Student must be a CS Student.}
\UseCaseNonFunctionalRequirements{}
\UseCaseScenarios{Student notifies Course Coordinator.}
\UseCaseRisks{We do not know if this must integrate with the current 
 database or not. We do not know if the student will recieve 
 confirmation by the Coordinator of receipt of this notification. We 
 do not know if the student has to show proof of success.}
\UseCaseUserInterface{Student Notification Screen.}
\end{UseCaseTemplate}
